\documentclass[11pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\input{preamble} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Aaron Purnomo Murniadi}{}  % Your name and date of birth or subtitle

\noindent\bull\textsmaller{\href{mailto:aaronmurniadi@gmail.com}{\textit{aaronmurniadi@gmail.com}}}

\noindent\bull\textsmaller{+62} 881-535-9522 % Your phone number(s) and Skype username

\noindent\bull\textsmaller{\textit{\href{https://www.linkedin.com/in/aaronmurniadi/}{www.linkedin.com/in/aaronmurniadi}}}
%\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

% \begin{multicols}{2}  % Start a two-column layout
\noindent I have experience in QA Software Testing (Manual and Automation). In Cybersecurity, I have experience in discovering, documenting, and reporting two
major security flaws of both national and international websites (see \textit{Working Experience}). Technology, programming, and software development has always been my life-long passion.
On the sideline, I also promote the use of Free and Open Source Software (FOSS) and Open Science.

\vspace{-1em} % Reduce whitespace after the Summary heading and the two-column content
% \end{multicols}

%\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Working Experience} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{https://www.ninjavan.co/}{Ninja Van}}
{\dotfill\textsc{Full Time (Jan 2023--\textit{Present})}} {

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Software Engineer 1, QA}
    {}
    {\bodytext{
    \begin{itemize}
        \item Developed and maintained automation regression tests in \textit{Java}, including API testing with \href{https://rest-assured.io/}{REST Assured} and \href{https://square.github.io/okhttp/}{OkHttp} library, Web front-end testing using \href{https://www.selenium.dev/documentation/webdriver/}{Selenium WebDriver}, as well as Android testing using \href{https://github.com/appium/appium-flutter-driver}{Appium Flutter Driver}. The integrated test runner for all the above automation tasks was \href{https://github.com/cucumber/cucumber-jvm}{Cucumber-JVM}.
        \item Primary contributor and developer for the integration of \href{https://github.com/karatelabs/karate}{Karate DSL} into the testing suite utilized by the entire QA team.
        \item Designed and developed the ATS (API to Scenario) mapping system, providing visibility and source of truth into which scenarios are testing specific APIs. This involved creating a new API for a service written in \textit{Go}.
        \item Assisted in integrating OpenAPI-generated API clients into the automation framework.
    \end{itemize}
    }}

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Software Tester (Manual) \dotfill\textsc{Internship (Dec 2021--Dec 2022)}}
    {}
    {\bodytext{
    \begin{itemize}
        \item Conducted manual testing of new product changes and features.
        \item Created and implemented new testing scenarios in \href{https://studio.cucumber.io/}{Cucumber Studio}.
        \item Performed smoke testing in the production environment.
        \item Developed a Python project to assist manual testers in speeding up the testing process (semi-automated testing) using \href{https://github.com/behave/behave}{Behave} library.
    \end{itemize}
    }}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{https://www.pdcnet.org/}{Philosophy Documentation Center}}
{\dotfill\textsc{Remote Work (2019)}} {

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Freelance Bug Hunter}
    {}
    {\bodytext{Report and documentation of an backdoor exploit on their webpage front-end.}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{https://www.driyarkara.ac.id/}{Sekolah Tinggi Filsafat Driyarkara}}
{\dotfill\textsc{Remote Work (2020)}} {

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Freelance Bug Hunter}
    {}
    {\bodytext{Report and documentation of institutional data leak.}}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{}{Y3 Event and Wedding Organizer}}
{\dotfill\textsc{Cirebon, West Java (2016--2018)}} {

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Time Keeper}
    {}
    {\bodytext{Overseeing the event schedule. Wake-up call to clients and families.
            Follow up calls to food catering, building management,
            Make-Up Artists, and other third party associates.}}

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Count Keeper}
    {~}
    {\bodytext{Keeping accurate count of guests and sending updates to the team so they could act accordingly.}}

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Receptionist}
    {~}
    {\bodytext{Welcoming the guests of the event. Provide basic information and assistance for guests.
            Responsible for the safety of the gifts that are meant for the client.}}
}

%------------------------------------------------

%------------------------------------------------

%\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Software}{} {
    \headedsubsection % Job title entry for the current employer
    {Git, VS Code, JetBrain's IntelliJ, Postman, DBeaver, Office 365, Adobe Photoshop and Lightroom, Google Workspace, LaTeX, Python, Java, SQL, Golang.}{}{}
}

\headedsection
{Operating System}{} {
    \headedsubsection % Job title entry for the current employer
    {Windows XP-11, MacOS, Ubuntu, Manjaro, ArchLinux, Fedora, Android.}{}{}
}

\headedsection
{Web and Cloud}{} {
    \headedsubsection % Job title entry for the current employer
    {GitHub, GitLab, WordPress, Vercel, Netlify.}{}{}
}

\headedsection
{Language}{} {
    \headedsubsection % Job title entry for the current employer
    {Bahasa Indonesia (native), English (Intermediate Reading, Writing, Listening, and Active Speaking).}{}{}
}
%------------------------------------------------
%----------------------------------------------------------------------------------------

\roottitle{Portfolio} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\textit{This CV You're Reading}}
{} {
\headedsection{{}}{}{
\bodytext{This document is written in \href{https://www.latex-project.org/}{\LaTeX{}} and hosted on \href{https://www.github.com/aaronmurniadi/cv}{GitHub}. It utilizes GitHub's \textit{Action} feature as part of Continuous Deployment system (the practice of using automation to publish and deploy software update). For every commit to the \texttt{[main]} branch, the build for this document will be triggered and then deployed as a new release. It's also available on \href{https://www.overleaf.com/read/vnhthngdyqnh}{Overleaf} for both preview and code changes.
}}
}

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{}{SMAK BPK Penabur Cirebon}}
{\dotfill\textsc{Cirebon, West Java (2014--2017)}} {

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Student Commitee in: }
    {}
    {\bodytext{\textit{Festival Drama Cerita Rakyat} (2015 \& 2016), \textit{Science Week} (2015), \textit{Shiki Matsuri Hanami Japanese Festival} (2016), \textit{Student Introduction Program} (2016), \textit{Live In: Muntilan} (2016).}}

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Table Tennis Athlete}
    {~}
    {\bodytext{Semi-finalist in POPKOT (Pekan Olahraga Pelajar Tingkat Kota) 2016,\\ Kota Cirebon.}}

    \headedsubsection % Job title entry for the current employer
    {\acr{as} Programming Competition Finalist}
    {~}
    {\bodytext{Finalist of ANFORCOM (Annual Informatics Competition) 2017, \\Diponegoro University, Kota Semarang}}
}

\vfill

\begin{flushright}
    \textit{
        ``It is not the strongest of the species that survives, nor the most intelligent;\\it is the one most adaptable to change.'' — \textsc{Charles Darwin}}
\end{flushright}

\vfill

\vfill

{
\footnotesize\noindent
    The latest version of this document is available at:\\\href{https://github.com/aaronmurniadi/cv/releases}{https://github.com/aaronmurniadi/cv/releases}
}
\end{document}
